Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-17 Paper2015.tex
Changed title to that upon which we agreed in January.
General editing

\title{
    Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL
}

@@

\maketitle % Insert title
\todo{Check title, affiliations etc.}

@@

\subsection{Neutrons}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the present calculations by 31\%.

@@

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev14}.
The parameterisation therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP and SUP}

Neutron beam monitoring and characterisation at TSL includes measurements with \U238\ TFBCs~\cite{Prokofiev14}.
Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements~\cite{Prokofiev14}.
In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{
        Neutron profile at the CUP, normalised to fluence rate on axis.
        \SI{10.2}{\cm} collimator}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
    \caption{
        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} collimator
        }
    \label{fig:TOFSpectra}
\end{figure}

Fig.~\ref{fig:Lethargyplots} compares calculates spectra at SUP and CUP with their respective standard facility models~\cite{Prokofiev2009,Prokofiev14}.
The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
The results show\ldots
\todo{Describe the neutron spectra.}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{
            SUP.
            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{
            CUP.
            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
	\caption{
        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
        \SI{10.2}{\cm} collimator
    }
	\label{fig:Lethargyplots}
\end{figure}

Fig.~\ref{fig:DifferentialSpectra} summarise neutron yield results by comparing differential flux as calculated in this work with facility parameterisations~\cite{Prokofiev2009,Prokofiev14}.
The SUP calculations and parameterisations agree very closely below \SI{20}{\MeV}; the parameterisation exceeds the calculations somewhat above that energy.
At CUP the parameterisation exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
\todo{Improve precision of the summary description of differential spectra.}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} collimator), comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{Standard User Position}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{Close User Position}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{
        Calculated gamma spatial distribution.
        \SI{10.2}{\cm}collimator
    }
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{
        Calculated gamma spectra at CUP and SUP.
        \SI{10.2}{\cm} collimator
    }
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{Standard User Position}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{Close User Position}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{
        Calculated gamma dose spectra.
        \SI{10.2}{\cm} collimator
    }
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

\title{
    Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities
}

@@

\maketitle

@@

\subsection{Neutrons}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2009}.
The analytical model therefore exceeds the present calculations by 31\%.

@@

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev14}.
The analytical model therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP and SUP}

Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs~\cite{Prokofiev14}.
In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{
        Neutron profile at the CUP, normalised to fluence rate on axis.
        \SI{10.2}{\cm} diameter collimator}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
    \caption{
        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator
        }
    \label{fig:TOFSpectra}
\end{figure}

Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models~\cite{Prokofiev2009,Prokofiev14}.
The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
The results show\ldots
\todo{Describe the neutron spectra.}

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{
            SUP.
            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against an analytical model~\cite{Prokofiev2009}
        }
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{
            CUP.
            The comparison is against the a standard analytical model~\cite{Prokofiev2009}
        }
    \end{minipage}
	\caption{
        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
        \SI{10.2}{\cm} diameter collimator
    }
	\label{fig:Lethargyplots}
\end{figure}

Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with analytical models~\cite{Prokofiev2009,Prokofiev14}.
The SUP calculations and analytical models agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
At CUP the analytical model exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
\todo{Improve precision of the summary description of differential spectra.}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} diameter collimator), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{Standard User Position}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{Close User Position}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{
        Calculated gamma spatial distribution.
        \SI{10.2}{\cm} diameter collimator
    }
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{
        Calculated gamma spectra at CUP and SUP.
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{Standard User Position}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{Close User Position}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{
        Calculated gamma dose spectra.
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:GammaDoseEnergy}
\end{figure}
